\Title

### 2020-12-15 manuscript/manuscript.tex
Don't include definition of observation points a second time

\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
values of the observed field at the observation points ${\mathbf{p}_i}_{i=1}^N$,
$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
whose elements are

>>>>

\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
values of the observed field at the observation points,
$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
whose elements are
